Contention Management for 5G

### 2017-02-09 article/article.tex

	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $Dl(u,v) \geq 1$ that we call the delay and
	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie

      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.

      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} Dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.

@@

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.

@@

@@

      Thus, the whole proccess time for a vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
      $$

@@

      \noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}

@@

      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?

>>>>

	We consider a directed graph $G=(V,A)$ modelling a network. Each arc  $(u,v)$ in $A$ is labeled by an integer $dl(u,v) \geq 1$ that we call the delay and
	which represents the number of time slots taken by a signal to go from $u$ to $v$ using this arc. 
	%Note that for any arc $(u,v)$, $Dl(u,v)=Dl(v,u)$. Dominique voulait être plus général, on mettera cette propriété dans notre topologie

      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. 
      We will often refer to the first element of the route as a source and the last as a target.

      The {\bf latency} of a vertex $u_i$ in $r$, with $i \geq 1$, is defined by $$\lambda(u_i,r)= \sum\limits_{0 \leq j <i} dl(a_j)$$ We also define $\lambda(u_0,r)=0$.
      The latency of the route $r$ is defined by $\lambda (r)= \lambda (u_k,r)$.

@@

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.

      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any odd $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}

      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R_{\cal C}}$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network

      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.

@@

%       \begin{center}
%       \includegraphics[scale=0.2]{rrh.jpeg}
%       \end{center}
%       
%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
%       
%        \begin{center}
%       \includegraphics[scale=0.2]{BBU1.jpeg}
%       
%       \includegraphics[scale=0.2]{BBU2.jpeg}
%       \end{center}
%

@@

      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
      $$

@@

      \noindent {\bf Periodic Assignment for Low Latency(PALL)}

@@

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}$ such that $MT({\cal M}) \leq T_{max}$?
